The \project{unRAVE} catalog

### 2016-09-02 article/unrave.tex
Explicitly write out our (highest-level) assumptions /ping @davidwhogg

%\AuthorCallLimit=10

@@

\begin{abstract}
The Milky Way may be our greatest laboratory for understanding galaxy formation.
This premise relies on the ability to precisely determine the astrometry and
chemistry for many individual stars, and to use those data to make inferences
about the Galaxy's formation and evolution. On 14 September 2016 the \gaia\ 
mission will release precise astrometry for $\approx2\times10^6$ stars.  
However, a comprehensive catalog of detailed chemical abundances to complement
those data is currently lacking.  The RAdial Velocity Experiment (\rave) survey 
has acquired spectra for 292,036 stars in common with the first \gaia\ data 
release, constituting the largest overlap of any stellar spectroscopic sample.  
Here we perform an independent analysis of \rave\ spectra using an implementation
of \thecannon\ that uses prior probabilities on atomic line formation and stellar
astrophysical parameters.  Our approach yields precise stellar labels at lower 
S/N ratios than most \emph{ab initio} approaches, allowing us to deliver improved
radial velocities, effective temperature $\teff$, surface gravity $\logg$, and 
chemical abundances of up to seven elements (Mg, Al, Si, Ca, Ti, Fe, Ni) for 
\Nstars\ stars.  We validate our results internally from repeat visits, and 
externally against existing high-resolution spectroscopic surveys.  The typical
precision in chemical abundances is X.XX~dex.  We provide spectrophotometric 
distances based on our labels, improving upon the parallax distances available
for the fainter targets in the first \gaia\ data release. \stub{A one-line 
science result based on RAVE/Hipparcos overlap}
\end{abstract}

@@

Throughout this work we adopt the assumptions and nomenclature first set out in
\citet{Ness_2015}, and extended in \citet{Casey_2016b}.  However, one distinction 
here with \citet{Casey_2016b} is that in this work the \emph{labelled} set and the
\emph{training} set will be the same set.  In \citet{Casey_2016b} two subsets of
the labelled set were defined: the training set and a distinct validation set.
This allowing us to train on the \emph{training set} and then test on the 
\emph{validation set}.  However in this work the labelled set is relatively 
small, about an order of magnitude smaller than what was available in 
\citet{Casey_2016b}, and therefore no validation set exists. We will use all 
labelled set stars in the training step and supplement our validation experiments 
with literature comparisons.  Thus, throughout this work we will use the terms 
\emph{labelled set} and \emph{training set} interchangeably.  Below we describe 
how we constructed the training set, before we outline the models that we adopt.

>>>>

% For AASTeX v6
%\AuthorCallLimit=10
%\fullcollaborationName{The \rave\ Collaboration}

@@

\begin{abstract}
The Milky Way may be our greatest laboratory for understanding galaxy formation.
This premise relies on the ability to precisely determine the astrometry and
chemistry for many individual stars, and to use those data to make inferences
about the Galaxy's formation and evolution. On 14 September 2016 the \gaia\ 
mission will release precise astrometry for $\approx2\times10^6$ stars.  
However, a comprehensive catalog of detailed chemical abundances to complement
those data is currently lacking.  The RAdial Velocity Experiment (\rave) survey 
has acquired spectra for 292,036 stars in common with the first \gaia\ data 
release, constituting the largest overlap of any stellar spectroscopic sample.  
Here we perform an independent analysis of \rave\ spectra using an implementation
of \thecannon\ that uses prior probabilities on atomic line formation and stellar
astrophysical parameters.  Our approach yields precise stellar labels at lower 
S/N ratios than most \emph{ab initio} approaches, allowing us to deliver improved
radial velocities, effective temperature $\teff$, surface gravity $\logg$, and 
chemical abundances of up to seven elements (O, Mg, Al, Si, Ca, Fe, Ni) for 
\Nstars\ stars.  We validate our results internally from repeat visits, and 
externally against existing high-resolution spectroscopic surveys.  The typical
precision in chemical abundances is X.XX~dex.  We provide spectrophotometric 
distances based on our labels, improving upon the parallax distances available
for the fainter targets in the first \gaia\ data release. \stub{A one-line 
science result based on RAVE/Hipparcos overlap}
\end{abstract}

@@

\noindent{}Our work makes the following assumptions about the \rave\ spectra and \thecannon:

\begin{itemize}
\item We will assume that any fibre- and time-dependent variations in spectral
resolution in the \rave\ spectra are negligible.
\item The \rave\ noise variances are approximately correct, independent between
pixels, and normally distributed.
\item We assume that the normalization procedure employed by the \rave\ pipeline
is invariant with respect to the labels, and invariant with respect to the S/N
ratio.
\item We assume that stars with similar labels ($\teff$, $\logg$, and abundances)
have similar spectra.
\item A stellar spectrum is a smooth function of the label values for that star,
and we assume that the function is smooth enough within a sub-space of the labels
(e.g., the giant branch or the main-sequence) that it can be reasonably approximated 
with a low-order polynomial in label space.
\item We have constructed a training set of stars with mean accurate labels.  Note
that we do not assume that \emph{every} label in the training is accurate -- we can
afford to have a small fraction of inaccurate labels (e.g., unambiguous misclassifications
present in the training set).
\item We assume our training set is representative of the test set (the \rave\ survey).
\end{itemize}

We adopt the nomenclature first set out in \citet{Ness_2015}, and extended in 
\citet{Casey_2016b}.  However, one distinction here with \citet{Casey_2016b} is 
that in this work the \emph{labelled} set and the \emph{training} set will be 
the same set.  In \citet{Casey_2016b} two subsets of the labelled set were 
defined: the training set and a distinct validation set.  This allowing us to 
train on the \emph{training set} and then test on the \emph{validation set}.  
However in this work the labelled set is relatively small, about an order of 
magnitude smaller than what was available in \citet{Casey_2016b}, and therefore 
no validation set exists. We will use all labelled set stars in the training 
step and supplement our validation experiments with literature comparisons.  
Thus, throughout this work we will use the terms \emph{labelled set} and 
\emph{training set} interchangeably.
